---
output:
    html_notebook:
        toc: true
        toc_float: true
editor_options:
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
library(devtools)
```

# `mctq` - package review

## **Reviewer:** [\@jonkeane](https://github.com/jonkeane)

### Review Submitted:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report contains documents associated with the review of **rOpenSci** submitted package:

### **`mctq`: ropensci/software-review**  issue [\#434](https://github.com/ropensci/onboarding/issues/434).

<br>

## Package info

**Description:**

A complete and consistent toolkit to process the Munich
    ChronoType Questionnaire (MCTQ) for its three versions (standard,
    micro, and shift).

**Author:** `r 
    c(person(given = "Daniel",
             family = "Vartanian",
             role = c("aut", "cre", "cph"),
             email = "danvartan@gmail.com",
             comment = c(ORCID = "0000-0001-7782-759X")),
      person(given = "Ana Amelia",
             family = "Benedito-Silva",
             role = c("aut", "sad"),
             email = "aamelia@usp.br",
             comment = c(ORCID = "0000-0003-4976-2623")),
      person(given = "Mario",
             family = "Pedrazzoli",
             role = c("aut", "sad"),
             email = "pedrazzo@usp.br",
             comment = c(ORCID = "0000-0002-5257-591X")),
      person(given = "Interdisciplinary Sleep Research Group (GIPSO)",
             role = c("fnd", "cph")),
      person(given = "University of Sao Paulo (USP)",
             role = "fnd"))`

**repo url:** <https://github.com/gipsousp/mctq>

**website url:** <http://gipsousp.github.io/mctq>

## Review info


#### See [reviewer guidelines](https://ropensci.github.io/dev_guide/reviewerguide.html) for further information on the rOpenSci review process.

**key review checks:**

- Does the code comply with **general principles in the [Mozilla reviewing guide](https://mozillascience.github.io/codeReview/review.html)**?
- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
- Are there **improvements** that could be made to the **code style?**
- Is there **code duplication** in the package that should be reduced?
- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?
- Is the [**documentation**](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) **clear and sufficient**?

Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://ropensci.github.io/dev_guide/policies.html#code-of-conduct) is mandatory for everyone involved in our review process.

***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "/Users/jkeane/repos/mctq"
```

## Test installation

### test local `mctq` install:

```{r test-local}
install(pkg_dir, dependencies = T, build_vignettes = T)
```

```{r github-rm}
remove.packages("mctq")
```
#### **comments:**

<!-- record comments on local install here -->

***

### test install of `mctq` from GitHub with:

```{r test-github}
devtools::install_github("gipsousp/mctq", dependencies = T, build_vignettes = T)
```

#### **comments:**

<!-- record comments on github install here -->

***



## Check package integrity

### run checks on `mctq` source:

```{r check-checks}
devtools::check(pkg_dir)
```
#### **comments:**

<!-- record comments on checks here -->

***

### run tests on `mctq` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

<!-- record comments on tests here -->

***


### check `mctq` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

<!-- record comments on goodpractice here -->

***

## Check package metadata files

### inspect

- #### [README](https://github.com/gipsousp/mctq)
- #### [DESCRIPTION](https://github.com/gipsousp/mctq/blob/master/DESCRIPTION)
- #### [NAMESPACE](https://github.com/gipsousp/mctq/blob/master/NAMESPACE)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

<!-- record comments on metadata files here -->

***

## Check documentation

online documentation: **<http://gipsousp.github.io/mctq>**

* Is the [documentation](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) clear and sufficient?

### test `mctq` function help files:

```{r test-help}
help(package = "mctq")
```

#### **comments:**

<!-- record comments on help files here -->

***

### test `mctq` vignettes:

```{r test-vignettes}
vignette(package = "mctq")
```

#### **comments:**

<!-- record comments on vignettes here -->

***

## Test functionality:

- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?

```{r free-style}
library("mctq")
```

```{r parse-functions}
exports <-ls("package:mctq")
exports
```

<!-- experiment with package functions -->

```{r exp-chunk}


```

#### **comments:**

<!-- record comments on package experimentation here -->

***

## Inspect code:

- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
    * good [function & variable naming?](https://ropensci.github.io/dev_guide/building.html#function-and-argument-naming)
    * good [dependency management](https://ropensci.github.io/dev_guide/building.html#package-dependencies)?
- Are there **improvements** that could be made to the [**code style?**](https://ropensci.github.io/dev_guide/building.html#code-style)
- Is there **code duplication** in the package that should be reduced?

```{r inspect-code}
pkgreviewr::pkgreview_print_source("mctq")
```
**\* might not be suitable for large packages with many exported functions**


<br>
<br>

#### **comments:**

<!-- record comments on package source code here -->


## Review test suite:

See guidance on [testing](https://ropensci.github.io/dev_guide/building.html#testing) for further details.

### test coverage

```{r pkg_coverage}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://github.com/gipsousp/mctq/blob/master/tests/testthat)


#### **comments:**

<!-- record comments on testing suite here -->


***
